CRUSE to Safe Cycling in Ireland

### 2023-09-29 paper.qmd
Tweak abstract

  To address data needs for both safety, business case development and project evaluation on the National Road Network (NRN), the Cycle Route Uptake and Scenario Estimation (CRUSE) Tool was developed.
  While cycling in Ireland represents only 3% of total modal share, with higher intensities in urban areas, the levels of cycling collisions are disproportionately high at 20% of all serious injuries and 7% of all fatalities.
  If Ireland is to meet its climate and safety targets, data to establish baseline cycling levels and future cycling levels is needed.

>>>>

  To address data needs for both safety, business case development and project evaluation on the National Road Network (NRN), the Cycle Route Uptake and Scenario Estimation (CRUSE) Tool was developed.
  Cycling in Ireland represents only 3% of total modal share as of the latest Census (2016), but accounts for 20% of serious injuries and 7% of all fatalities.
  High resolution datasets on baseline and potential cycling levels are needed to meet Ireland's climate and safety targets.
